Examples of functions

### 2024-08-21 README.Rmd
updating

# criticalvalue

@@

You can install the development version of criticalvalue like so:

``` r
# require(devtools)
devtools::install_github("filippogambarota/criticalvalue")
```

>>>>

# criticalESvalue

@@

You can install the development version of criticalESvalue like so:

``` r
# require(devtools)
devtools::install_github("psicostat/criticalESvalue")
```
